Stable Hot Spot Analysis (Draft)

### 2017-06-17 paper-main.tex
added quantile-based images to latex

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{
      Aggregation levels computed from original raster (log scale)
    }\\
    \hline
    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
  \end{tabular}

  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
%  \includegraphics[width=.45\linewidth]{images/gen-???}
%  \hspace{1em}
%  \includegraphics[width=.45\linewidth]{images/gen-???}

@@

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
  \end{tabular}

  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}

>>>>

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{
      Aggregation levels computed from original raster (log scale)
    }\\
    \hline
    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}

  \vspace{1em}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}\\

    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}\\

  \end{tabular}

  \vspace{1em}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}\\

    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-8}\\
  \end{tabular}

  \vspace{2em}
  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}

@@

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
  \end{tabular}

  \vspace{1em}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}\\

    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-8}\\
  \end{tabular}

  \vspace{1em}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}\\

    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-8}\\
  \end{tabular}

  \vspace{2em}
  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
